QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline

### 2023-11-10 minos/testing/QALY_comparison_energyCrises.Rmd
Switch to visualise glasgow synthetic runs

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')

>>>>

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')

### 2023-11-10 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Switch to visualise glasgow synthetic runs

```{r}
# # read in QALY files for baseline and interventions
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'default_config')

>>>>

```{r}
# # read in QALY files for baseline and interventions
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'default_config')
